%!TEX TS-program = ../make.zsh

\section{Introduction}
\label{sec:intro}

\icecube is a neutrino observatory located at Earth's South Pole.
It uses a cubic-kilometer of glacial ice as detector medium where secondary particles from neutrino interactions produce light as they move through the ice, which is then detected by an array of photo detector modules that are deployed throughout the ice. \cite{evidence2013}

The primary scientific objective of \icecube is the study of neutrinos with energies ranging from $10\TeV$ to $10\PeV$ produced in astrophysical processes, and the identification and characterization of their sources. In collaboration with optical, x-ray, gamma-ray, radio, and gravitational-wave observatories, it is an important part of multi-messanger astronomy. Other objectives include the indirect detection of dark matter, the search for other exotic particles, and the study of neutrino-oscillation physics. \cite{instrumentation, evidence2013}

As \icecube detects neutrinos indirectly through the interaction with other particles, involving a chain of processes, a key requirement for precise measurements is to minimize uncertainties for each process and component involved. Some components such as technical instruments in the detector modules can be tested and calibrated in isolation in laboratories. Other components involved such as the glacial ice cannot be extracted and need to be studied where they are. Uncertainties concerning the properties of the glacial ice can effect the precision for measurements of the direction of the detected neutrinos by several percent. \cite{wrede}

All light that is detected by the detector modules needs to travel through the refrozen water of the drill holes that were needed to deploy the detector modules within the ice. This so called \textit{hole ice} may have properties significantly different from the surrounding bulk ice regarding the propagation of light through this medium. The properties of the hole ice, however, are less known than the properties of the bulk ice and pose the largest systematic uncertainty for study of neutrino oscillations and a number of other analyses. \cite{icrc17pocam}

This study aims to provide the necessary tools to improve detector calibration by introducing the means to simulate the propagation of light through the hole ice. By comparing different simulation scenarios, involving hole ice of different respective properties, to calibration data, it is then possible to study the properties of the hole ice and its effect on the propagation and detection of light by the detector modules, reducing the systematic uncertainties imposed by the hole ice, and in the long run improving the precision of the \icecube observatory.

After providing some background information in sections \ref{sec:theoretical_background} to \ref{sec:simulation_background}, two algorithms and their integration into the existing \icecube software framework will be presented in section \ref{sec:methods} that allow to simulate the direct propagation of photons through hole ice of different properties. The validity of the algorithms will be supported by a series of tests and cross checks in section \ref{sec:unit_tests_and_cross_checks}.

Examples of application such as the simulation of one or several hole-ice cylinders with different sizes and photon scattering lengths, the simulation of shadowing cables, and a calibration method using LED flasher data are given in section \ref{sec:applications}. Section \ref{sec:discussion} presents a brief comparison of methods and preliminary results to other studies.

The material needed to reproduce this study is provided on the accompanying cd rom and can be found online at \url{https://github.com/fiedl/hole-ice-study}.

