%!TEX TS-program = ../make.zsh

\section{Theoretical Backtround}
\label{sec:theoretical_background}

## Neutrinos
## Neutrino Interactions Relevant to IceCube
## Cherenkov-light Emission
- wave length: visible, near uv
- see \cite{ppcpaper}, section 1

\subsection{Photon Absorption and Scattering}
\label{sec:scattering}

The propagation of light through a medium depends on the optical properties of that medium, in particular the velocity of light within that medium, the scattering probability and the absorption probability. \cite{lundberg}
% lundberg, page 4

The absorption of light for the relevant wavelength range is caused by electronic and molecular excitation processes \cite{lundberg}
% lundberg, page 4
and is quantified by the \textbf{absorption length} $\lambda\abs$, which is the mean of the exponentially distributed free path length to absorption \cite{lundberg}.
% lundberg
Therefore, in accordance with the \noun{Beer-Lambert law}, the absorption length is the path length that light needs to travel within a medium to have its intensity drop to $\sfrac{1}{\e}$ of its original intensity. \cite{lexikonderphysik}
% lexikonderphysik, Band 1, Absorptionslänge
% Absorption lengths in the south-polar ice are in the order of $100\m$ and can in clear ice layers in the absence of dust even exceed $200\m$. \cite{ackermann}
% ackermann, page 5, paragraph 12
Absorption lengths in the south-polar ice vary between $20\m$ in dusty regions and $280\m$ in very clear ice layers. \cite{ackermann}\cite{ppcpaper}\cite{icepaper}

The scattering of light off microscopic scattering centers, such as submillimeter-sized air bubbles and micron-sized dust grains \cite{Price1997}\cite{ackermann} is the dominant scattering mechanism in glacial ice \cite{Askebjer1997}\cite{lundberg}. This scattering can be modelled using the more general \noun{Mie scattering} theory, which describes the scattering of electromagnetic radiation off small, spherical masses of material with refractive indices differing from the refractive index of its surroundings. \cite{Mie1908}\cite{ackermann}\cite{lundberg}

\noun{Mie scattering} gives the distribution of the scattering angle $\theta$ for any wavelength and scattering center size. For ice, this distribution is approximated using a one-parameter \noun{Henyey-Greenstein} (HG) phase function $p_\text{HG}(\theta; \tau)$, where the one parameter $\tau$ is the mean cosine of the scattering angle. \cite{lundberg}

\newcommand\meancostheta{\langle \cos \theta \rangle}
$$ p_\text{HG}(\theta; \tau) = \frac{1 - \tau^2}{2(1 + \tau^2 - 2\tau\, \cos \theta)^\frac{3}{2}}, \ \ \ \tau = \meancostheta $$

The south-polar ice has shown to be preferentially forward scattering with a mean cosine of the scattering angle of $\meancostheta = 0.94$ with only a weak dependence on the wavelength. \cite{ackermann}
% ackermann, paragraph 9

The \textbf{scattering length} $\lambda\sca$, which is also called \textbf{geometric} scattering length, is the mean of the exponentially distributed free path and thereby the average distance between scatterings. \cite{ackermann}

% https://github.com/fiedl/hole-ice-study/issues/52 - Effective scattering length
A related and often used quantity is the \textbf{effective scattering length} $\lambda\esca$, which is the distance that light needs to propagate through a turbid medium before the photon directions are completely randomized. \cite{lundberg}

\begin{equation}
  \lambda\esca = \frac{\lambda\sca}{1 - \meancostheta}
\end{equation}

In a medium with isotropic scattering, the geometric and the effective scattering length are the same. In a preferentially forward scattering medium like the south-polar ice, the original direction of a sample of photons is tendentially retained for several scattering steps until the photon direction of the sample is isotropized. The projection of the net velocity vector on the original direction is decreased on average by $\meancostheta$ for each scattering. \cite{lundberg}

After $n$ scatterings, the effectively transported forward distance along the original direction is $\lambda\sca\,\sum_{i=0}^n \meancostheta^i$, such that in the limit of many scatterings, $n \rightarrow \infty$, the effectively transported forward distance becomes the effective scattering length. \cite{lundberg}\cite{ackermann}

$$ \lim_{n \rightarrow \infty} \lambda\sca\,\sum_{i=0}^n \meancostheta^i = \frac{\lambda\sca}{1 - \meancostheta} = \lambda\esca $$

% Typical scattering length:
% average esca = 25m \cite{lundberg}
% scattering lengths between 5m and 90m in the detector volume \cite{ppcpaper}
% effective scattering coefficient for 400nm between 0.011/m and 0.2/m \cite{icepaper} fig. 16, corresponding to esca=5m to 90m esca

Typical effective scattering lengths within the south-polar ice are in the order of $25\m$ \cite{lundberg} and range from $5\m$ to $90\m$ in the detector volume \cite{icepaper}, corresponding to the geometric scattering length ranging from $30\cm$ to $5.4\m$.

% https://github.com/fiedl/hole-ice-study/issues/51 - point particles
Light interference effects are ignored during photon propagation as the average distance between the scattering centers is large compared to the photon wavelength. \cite{ackermann}

Also, despite modelling different ice regions with abrupt boundaries in the simulations of this study, the physical boundaries are assumed such that refractive index variations are continuous. Hence reflection at the medium boundaries is ignored in simulations. \cite{lundberg}
